Considering scale in multilayer animal social networks

### 2020-06-22 paper/manuscript.Rmd
mv up temp, nobs

@@

The effect of seasonality of resources on sociality can be directly measured by
differences across discrete time windows. Using an ordinal multilayer network
consisting of 20 discrete time windows throughout the study period, we observed
periods of increased sociality in caribou on Fogo Island (Figure \@ref(fig:temp)). 
Edge overlap was higher between approximately October and May
(time windows 1, 6-11, 15-20) compared to between approximately May and October
(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A). These periods of high edge
overlap correspond to seasons of low resource availability [Peigner_2019].
Similarly, individual graph strength was also highest in these periods (Figure
\@ref(fig:temp) B). By explicitly considering the temporal context of social interactions
in separate layers, multilayer networks provide a detailed and dynamic perspective at
animal social networks.

Selection of appropriate time windows is essential for capturing sociality in specific
life stages of interest. Social phenotypes can change over ontogeny in ways that
can affect fitness [@Berger_2015; @Brent_2017]. Further complicating the issue,
individuals can vary in their rate of development [@Tarka_2018]. This variation
can make defining the appropriate temporal scale for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny difficult. However, considering fine temporal scales has been show to
provide insight across developmental stages that may otherwise be missed
[@Turner_2017] <!-- It would be better to cite the more recent one if it gets released in time. --> 
Furthermore, given the non-independent nature of social
interactions and associations, especially over time, it can be challenging to
test hypotheses about social dynamics with a suitable null control
[@Farine_2017; @Proskurnikov_2017]. Using the framework of multilayer networks,
ordinal layers of discrete time windows provide a way to make appropriate null
models to test questions about the dynamics of an individual’s social network
position over multiple aggregated time periods.

Finally, it is crucial to consider sufficient data to construct robust networks
when selecting time windows and study periods. Time windows should be long
enough for each layer to have enough data for robust networks [@Farine_2017]. To
test the influence of data quantity on multilayer networks, we used a subset of
observations to generate multilayer networks. All network metrics across all
three habitat layers appeared to stabilize with increasing number of
observations. Individual graph strength showed high variability at low number of
observations, while edge overlap and multidegree increased sharply. After
approximately 200 observations, the rate of change for all metrics decreased and
and graph strength remained relatively static, while edge overlap and
multidegree continued to increase slowly. As more observations were added, more
and rarer relationships were recorded revealing the value of this form of
sensitivity analysis.

>>>>

<!-- temp -->
The effect of seasonality of resources on sociality can be directly measured by
differences across discrete time windows. Using an ordinal multilayer network
consisting of 20 discrete time windows throughout the study period, we observed
periods of increased sociality in caribou on Fogo Island (Figure \@ref(fig:temp)). 
Edge overlap was higher between approximately October and May
(time windows 1, 6-11, 15-20) compared to between approximately May and October
(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A). These periods of high edge
overlap correspond to seasons of low resource availability [Peigner_2019].
Similarly, individual graph strength was also highest in these periods (Figure
\@ref(fig:temp) B). By explicitly considering the temporal context of social interactions
in separate layers, multilayer networks provide a detailed and dynamic perspective at
animal social networks.

Selection of appropriate time windows is essential for capturing sociality in specific
life stages of interest. Social phenotypes can change over ontogeny in ways that
can affect fitness [@Berger_2015; @Brent_2017]. Further complicating the issue,
individuals can vary in their rate of development [@Tarka_2018]. This variation
can make defining the appropriate temporal scale for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny difficult. However, considering fine temporal scales has been show to
provide insight across developmental stages that may otherwise be missed
[@Turner_2017] <!-- It would be better to cite the more recent one if it gets released in time. --> 
Furthermore, given the non-independent nature of social
interactions and associations, especially over time, it can be challenging to
test hypotheses about social dynamics with a suitable null control
[@Farine_2017; @Proskurnikov_2017]. Using the framework of multilayer networks,
ordinal layers of discrete time windows provide a way to make appropriate null
models to test questions about the dynamics of an individual’s social network
position over multiple aggregated time periods.
<!-- temp -->

<!-- nobs -->
Finally, it is crucial to consider sufficient data to construct robust networks
when selecting time windows and study periods. Time windows should be long
enough for each layer to have enough data for robust networks [@Farine_2017]. To
test the influence of data quantity on multilayer networks, we used a subset of
observations to generate multilayer networks. All network metrics across all
three habitat layers appeared to stabilize with increasing number of
observations. Individual graph strength showed high variability at low number of
observations, while edge overlap and multidegree increased sharply. After
approximately 200 observations, the rate of change for all metrics decreased and
and graph strength remained relatively static, while edge overlap and
multidegree continued to increase slowly. As more observations were added, more
and rarer relationships were recorded revealing the value of this form of
sensitivity analysis.
<!-- temp -->

@@
